Curriculum and Transfer Learning of Hierarchical Locomotion Policies

### 2018-06-04 paper/main.tex
Add initial 2d walker script
2dwalker.py contains code to run an two-step episode for a planar
walker. It also has code for a PD controller that can hold a target
pose.

We collect both quantitative and qualitative metrics to measure ``achieving better results''.
Quantitatively, we compare the average rate of forward progress.
We also consider the robustness of the model to force perturbations and various measures of the ``difficulty'' of the terrain (such as stair height).
Qualitatively, we document motion quality by means of supplementary videos, which we encourage the reader to consult.

@@

\textbf{Low-level actions.}
On the one hand, we could have low-level actions being the raw torques.
On the other hand, this might make the learning problem harder, so we could specify some more abstract actions and use PD controllers or other analytical formulas to derive the actual torques.
For instance, the output could be a target pose or end-effector position which is chosen more infrequently than the simulation framerate.
Then we could solve an inverse kinematics or inverse dynamics problem to calculate a target pose, which is then achieved using PD controllers.
\nhatch{We probably don't need all of this machinery.
For the initial proof of concept, it might make sense to see how we can do using just raw torques.}
\nhatch{TODO think about this some more.}

@@

>>>>

We collect both quantitative and qualitative metrics to measure ``achieving better results''.
Quantitatively, we compare the average rate of forward progress.
We also consider the robustness of the model to force perturbations and various measures of the ``difficulty'' of the terrain (such as stair height).
\footnote{Another interesting question would be robustness with respect to accuracy of perception.
If the potential step target locations / surface normals are perturbed, what happens?}
Qualitatively, we document motion quality by means of supplementary videos, which we encourage the reader to consult.

@@

\textbf{Low-level actions.}
On the one hand, we could have low-level actions being the raw torques.
On the other hand, this might make the learning problem harder.
Instead, we could specify ``abstract actions'' and use PD controllers or other analytical formulas to derive the actual torques.
For instance, the output could be a target pose or end-effector position which is chosen more infrequently than the simulation framerate.
Then we could solve an inverse kinematics or inverse dynamics problem to calculate a target pose, which is then achieved using PD controllers.
\nhatch{We probably don't need all of this machinery.
For the initial proof of concept, it might make sense to see how we can do using just raw torques.}
\nhatch{TODO think about this some more.}

@@

\textbf{Miscellaneous ideas.}
\begin{itemize}
  \item Could the HLC-LLC interface be in terms of a \emph{force} that the LLC should try to generate on the next foot contact?
  \item How can we design the LLC to generate good motion quality (e.g. low energy, low angular momentum)?
\end{itemize}
